---
title: "Places to See Cherry Blossoms in Seattle"
author: "Wan-Ling Hsu"
date: "3/30/2018"
output:
  html_document: default
  pdf_document: default
---
## Developing Data Products Week 2 Assignment 
### (Coursera - Data Science Specialization) 
### Instructions
Create a web page using R Markdown that features a map created with Leaflet.

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!

### Review criteria

The rubric contains the following two questions:

- Does the web page feature a date and is this date less than two months before the date that you’re grading this assignment?
- Does the web page feature an interactive map that appears to have been created with Leaflet?

### My Submissions

Here are several places you can see cherry blossoms around Seattle and enjoy walking through cherry trees to welcome Spring

* The quad at the University of Washington
* Washington Park Arboretum 
* Seward Park and Lake Washington Boulevard
* Jefferson Park

#### 1. Please click the blue icon on the map to find out the place's name.
```{r cherryBlossoms1}
# install.packages('devtools')
# devtools::install_github('rstudio/leaflet')
library(leaflet)
cherryBlossoms1 <- leaflet() %>%
        addTiles() %>%
        addMarkers(lat=47.657263, lng=-122.307198, popup="University of Washington Quad") %>%
        addMarkers(lat=47.637,    lng=-122.296   , popup="Washington Park Arboretum") %>%
        addMarkers(lat=47.556,    lng=-122.251   , popup="Seward Park and Lake Washington Boulevard") %>%
        addMarkers(lat=47.566611, lng=-122.307333, popup="Jefferson Park")

cherryBlossoms1

```


#### 2. Each place and its address shows on the map. Please click the place's name to link to the offical website to get relevant information. 
```{r cherryBlossoms2}
library(leaflet)
UW <- paste(sep = "<br/>",
  "<b><a href='https://www.washington.edu/news/2018/02/23/university-of-washington-cherry-blossom-watch-2018/'>
  University of Washington Quad</a></b>",
  "1400 NE Campus Pkwy",
  "King Ln  Pierce Ln",
  "Seattle, WA 98195"
)

Arboretum <- paste(sep = "<br/>",
  "<b><a href='https://botanicgardens.uw.edu/washington-park-arboretum/visit/'>
  Washington Park Arboretum</a></b>",
  "2300 Arboretum Dr E",
  "Seattle, WA 98112"
)

Seward <- paste(sep = "<br/>",
  "<b><a href='https://www.seattle.gov/parks/find/parks/seward-park'>
  Seward Park</a></b>",
  "5900 Lake Washington Blvd S",
  "Seattle, WA 98118"
)

Jefferson <- paste(sep = "<br/>",
  "<b><a href='https://www.seattle.gov/parks/find/parks/jefferson-park'>
  Jefferson Park</a></b>",
  "4101 Beacon Ave S",
  "Seattle, WA 98108"
)

cherryBlossoms2 <- leaflet() %>%
        addTiles() %>%
  addPopups(lat=47.657263, lng=-122.307198, popup = UW       , options = popupOptions(closeButton = FALSE)) %>%
  addPopups(lat=47.637,    lng=-122.296   , popup = Arboretum, options = popupOptions(closeButton = FALSE)) %>%
  addPopups(lat=47.556,    lng=-122.251   , popup = Seward   , options = popupOptions(closeButton = FALSE)) %>%
  addPopups(lat=47.566611, lng=-122.307333, popup = Jefferson, options = popupOptions(closeButton = FALSE))

cherryBlossoms2
```
